%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,9pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}



\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.575in}
\addtolength{\evensidemargin}{-0.575in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{0.8in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\makeatletter
\newlength{\bibhang}
\setlength{\bibhang}{0.1em} %1em}
\newlength{\bibsep}
 {\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
\newenvironment{bibsection}%
        {\begin{enumerate}{}{%
%        {\begin{list}{}{%
}
\small
        }
        {\end{enumerate}}
%        {\end{list}\vspace{-.6\baselineskip}}
\makeatother

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://www.lorabit.com/}{\Large Yanan Xie}} & Email : \href{mailto:lorabit@me.com}{lorabit@me.com}\\
  \href{http://lorabit.com/}{http://www.lorabit.com} & Mobile : +1-831-346-9038 \\
\end{tabular*}



%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
      {Rulai}{Campbell, California}
      {Senior AI Research Engineer}{Feb 2018 - Mar 2019}
      \resumeItemListStart
        \resumeItem{Multi-Round Conversational Database Querying}  
          {Designing and developing an easy-to-use product for designing data querying chatbot with dynamic flows. (as eng owner)}
        \resumeItem{Question Answering with Knowledge Graph}  
          {Exploring the latest natural language processing and machine learning techniques to build Rulai's knowledge graph module enabling AI chatbots to answer questions based on knowledge graphs. }
        \resumeItem{Vertical Library Creation}  
          {Building tools to collect data for creating vertical libraries. }
      \resumeItemListEnd

  \resumeSubheading
      {Google}{Mountain View, California}
      {Software Engineering Intern (I did get my conversion offer)}{Jun 2017 - Sep 2017}
      \resumeItemListStart
        \resumeItem{Data Migration}
          {Designed the process to migrate a table that was heavily used by multiple products from Google's internal KVS - Kansas to another internal DBMS - Spanner with zero downtime. The table serves several applications with different data consistency requirements. Developed and launched an independent service from scratch with several Google technologies - Apps Framework, Boq, Guice, Kansas, Protocol Buffer, Spanner. The service is used as an intermediary layer between applications and database to hide database migration process from applications.}
        \resumeItem{Data Processing}  
          {Used Google's planet-scale data processing tools to process massive log data.}
      \resumeItemListEnd

    \resumeSubheading
      {WithMe(Early Stage Startup)}{Hangzhou, China}
      {Founding Full-Stack Engineer, Team Leader}{Aug 2015 - Aug 2016}
      \resumeItemListStart
        \resumeItem{Prototyping}
          {Fast built an MVP(a hybrid app) in days to verify key business assumptions.}
        \resumeItem{Leadership}
          {Successfully led the iOS dev team of 3 delivering high-quality apps on time. Provided data structure and  algorithm training to all engineers inside the company.}
        \resumeItem{ORM Component}
          {Developed a thread-safe ORM component WMCache based on SQLite3 and Objective-C runtime methods. It is still used as a fundamental component in apps developed by WithMe.}
        \resumeItem{Data Synchronization}
          {Designed the basic data synchronization strategy, and implemented a multi-observer listener component which has significantly reduced the complexity of data logic, and is still used as a fundamental component.}
      \resumeItemListEnd

    \resumeSubheading
      {Alibaba}{Hangzhou, China}
      {Software Development Engineer (Top 10\% performer)}{Jun 2014 - May 2015}
      \resumeItemListStart
        % \resumeItem{Tech Stack}
        %   {Linux, PHP, Python, Redis, MySQL, MongoDB, JavaScript, and HTML}
        \resumeItem{Crowd-Sourcing Data Labeling System}
          {Built the whole system including the front end and back end. Implemented a random pre-assignment mechanism to implement a high-performance task distribution system, handling over 1,000,000 labeled data per day with a single server.}
        \resumeItem{Search Engine Debug and Test Toolbox}
          {Built several internal tools including stress simulation, search engine pipeline visualization and search result evaluation for search algorithm and machine learning teams. }
      \resumeItemListEnd

    \resumeSubheading
      {University of California, Santa Barbara}{Santa Barbara, CA}
      {Visiting Student}{May 2013 - Oct 2013}
      \resumeItemListStart
        \resumeItem{Natural Language Parser}
          {Built a knowledge-graph-based natural language parser for parsing nested sentences.}
        \resumeItem{Open Information Extraction}
          {Constructed knowledge graphs from witness statements by using named entity recognition, coreference resolution, and the parser.}
        \resumeItem{Quering Knowledge Graphs}
          {Developed an interactive knowledge graph explorer and a graph query composer with JavaScript and Java. Published a demo paper in SIGMOD 2014.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Santa Cruz}{Santa Cruz, CA}
      {Master of Science in Computer Science;  Advisor: Prof. Yi Zhang}{Sep. 2016 -- Dec. 2017}
       % \resumeItemListStart
       %  \resumeItem{Major courses}{Algorithm Analysis, Image Processing and Computer Vision, Design Database Systems, Data Mining}
       %  \resumeItemListEnd
    \resumeSubheading
      {Zhejiang University}{Hangzhou, China}
      {Bachelor of Engineering in Computer Science; Advisor: Prof. Jian Wu}{Sep. 2010 -- June. 2014}
       % \resumeItemListStart
       %  \resumeItem{Major courses}{C Programming, Database System, Data Structure, Artificial Intelligence, Computer Security}
       %  \resumeItemListEnd
  \resumeSubHeadingListEnd


\section{Skills}
  \resumeSubHeadingListStart
    \item{\textbf{AI and Data Science}
      {: Industrial experience with PyTorch and TensorFlow. Demos/papers accepted to top conferences like SIGMOD, CIKM, WWW, PAKDD.}
    }\\
    \textbf{Full-Stack Development}{:
      Unix/Linux, MySQL, MongoDB, Redis, PHP(Yii), NGINX, Java(Guava, Guice, Spring), gRPC(protobuf), Git, Docker, Jenkins, JavaScript(Vue.js, Koa), Photoshop, Objective-C.
    }\\
    \textbf{Product Management}{:
      Hands-on experience applying Lean Startup methodology to develop product iteratively and search for product/market fit.
    }
  \resumeSubHeadingListEnd


  
% \section{Publications}
% \begin{enumerate}
%   \small
%     \item Shengqi Yang, {\bf Yanan Xie}, Yinghui Wu, Tianyu Wu, Huan Sun, Jian Wu and Xifeng Yan.  ``SLQ: A User-friendly Graph Querying System." \emph{ACM SIGMOD Conference on Management of Data (SIGMOD 2014 Demo)}, Snowbird, Utah, USA. June 22 - 27, 2014.
%     \vspace{-5pt} \item {\bf Yanan Xie}, Liang Chen, Kunyang Jia, Lichuan Ji, Jian Wu.  ``iNewsBox: Modeling and Exploiting Implicit Feedback for Building Personalized News Radio." \emph{ACM Conference on Information and Knowledge Management (CIKM 2013 Demo)}, Burlingame, CA, USA. Oct 27 - Nov 1, 2013.
%     \vspace{-5pt} \item Jian Wu, Liang Chen, {\bf Yanan Xie}, Lichuan Ji, Zhaohui Wu.  ``Modeling and Exploring Historical Records to Facilitate Service Composition." \emph{International Journal of Web and Grid Services (IJWGS)}(accepted in April 2013).
%     \vspace{-5pt} \item Hanze Xu, {\bf Yanan Xie}, Dinglong Duan, Liang Chen, Jian Wu.  ``FTCRank: Ranking Components for Building Highly Reliable Cloud Applications." \emph{17th Pacific-Asia Conference on Knowledge Discovery and Data Mining (PAKDD 2013 Workshop)}, Gold Coast, Australia. April 14 - 17, 2013.
%     \vspace{-5pt} \item Jian Wu, Liang Chen, {\bf Yanan Xie}, Zibin Zheng. ``Titan: A System for Effective Web Service Discovery."  \emph{21th International World Wide Web Conference (WWW 2012 Demo)}, Lyon, France. April 16-20, 2012.
% \end{enumerate}


\end{document}
